Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-24 manuscript/draft.Rmd

**"Macroecological" model: richness GBM.** We used a boosted regression tree
model using the `gbm` package [@gbm] to directly model species richness
as a function of environmental variables. Boosted regression trees are a form of
tree-based modeling that work by fitting thousands of small tree-structured
models sequentially, with each tree optimized to reduce the error of its
predecessors. They are flexible models that are considered well suited for
prediction [@elith2008]. This model was optimized using a Gaussian likelihood,
with a maximum interaction depth of 5, shrinkage of 0.015, and up to 10,000
trees. The number of trees used for prediction was selected using the "out of
bag" estimator; this number averaged `r numbers$n_gbm[1]` for the non-observer
data and `r numbers$n_gbm[2]` for the observer-corrected data.

@@

All analyses were conducted using R [@R]. Primary R packages used in the
analysis included dplyr [@dplyr], tidyr [@tidyr], gimms [@gimms], sp [@sp1;
@sp2], raster [@raster], prism [@prism], rdataretriever [@rdataretriever],
forecast [@forecast1; @forecast2], git2r [@git2r], ggplot [@ggplot2], mistnet
[@harris2015], viridis [@viridis], rstan [@rstan], yaml [@yaml], purrr [@purrr],
gbm [@gbm], randomForest [@randomForest]. Code to fully reproduce this analysis
is available on GitHub (https://github.com/weecology/bbs-forecasting) and
archived on Zenodo (https://doi.org/10.5281/zenodo.839581).

>>>>

**"Macroecological" model: richness GBM.** We used a boosted regression tree
model using the `gbm` package [Ridgeway *et al.* -@gbm] to directly model
species richness as a function of environmental variables. Boosted regression
trees are a form of tree-based modeling that work by fitting thousands of small
tree-structured models sequentially, with each tree optimized to reduce the
error of its predecessors. They are flexible models that are considered well
suited for prediction [@elith2008]. This model was optimized using a Gaussian
likelihood, with a maximum interaction depth of 5, shrinkage of 0.015, and up to
10,000 trees. The number of trees used for prediction was selected using the
"out of bag" estimator; this number averaged `r numbers$n_gbm[1]` for the
non-observer data and `r numbers$n_gbm[2]` for the observer-corrected data.

@@

All analyses were conducted using R [@R]. Primary R packages used in the
analysis included dplyr [@dplyr], tidyr [@tidyr], gimms [@gimms], sp [@sp1;
@sp2], raster [@raster], prism [@prism], rdataretriever [@rdataretriever],
forecast [@forecast1; @forecast2], git2r [@git2r], ggplot [@ggplot2], mistnet
[@harris2015], viridis [@viridis], rstan [@rstan], yaml [@yaml], purrr [@purrr],
gbm [Ridgeway *et al.* -@gbm], randomForest [@randomForest]. Code to fully
reproduce this analysis is available on GitHub
(https://github.com/weecology/bbs-forecasting) and archived on Zenodo
(https://doi.org/10.5281/zenodo.839581).
